Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Add ref

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
\ref{sec:problem-discovery}.

@@

\newpage % FIXME
\subsection{hspec-discover}

As discussed in \ref{} we use a preprocessor to automatically generate
test drivers.  GHC invokes preprocessors with three arguments.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Automatic discovery of specs}
\label{sec:solution-discovery}
We want to automatically discover all specs of a project, so that we
can run them all together.  This requires to automatically generate
boilerplate code, similar to what is shown in
\ref{sec:problem-discovery}.

@@

\newpage % FIXME
\subsection{hspec-discover}
\label{sec:implementation-discovery}

As discussed in \ref{sec:solution-discovery} we use a preprocessor to automatically generate
test drivers.  GHC invokes preprocessors with three arguments.
